Principles for Open Data Curation: A Case Study with the New York City 311 Service Request Data

### 2024-09-08 manuscript/manuscript.tex
rephrased opening paragraph in cleansing sectoin

\section{Data Cleansing Issues} 
\label{sec:issues}
What is data cleansing?  Wikipedia 
\href{https://en.wikipedia.org/wiki/Data_cleansing}{Data Cleansing} 
offers this definition.

\begin{quote}\textit{Data cleansing or data cleaning is the process of detecting and 
correcting (or removing) corrupt or inaccurate records from a record set, 
table, or database and refers to identifying incomplete, incorrect, 
inaccurate or irrelevant parts of the data and then replacing, 
modifying, or deleting the dirty or coarse data.}
\end{quote}

>>>>

\section{Data Cleansing Issues} 
\label{sec:issues}

Data cleansing refers to the process of identifying and rectifying
errors, inconsistencies, and inaccuracies within datasets to ensure
they are of high quality and reliable for analysis
\citep{maletic2005data, hosseinzadeh2023data}. The process
typically involves removing duplicate records, handling missing or
incomplete data, correcting mislabeled or inaccurate entries, and
standardizing data formats. In the context of open data, cleansing is
especially important as open datasets often come from diverse,
uncoordinated sources, leading to variations in data quality,
completeness, and consistency. Without proper cleansing, the utility
of open data can be severely limited, affecting its reliability for
research, policy-making, and innovation. The main purpose of cleansing
open data is to ensure that it is accurate, consistent, and usable
across multiple platforms and by various stakeholders. This improves
the trustworthiness of the data and enables better decision-making,
more accurate analysis, and the integration of data into machine
learning models or other systems.

% What is data cleansing?  Wikipedia 
% \href{https://en.wikipedia.org/wiki/Data_cleansing}{Data Cleansing} 
% offers this definition.

% \begin{quote}\textit{Data cleansing or data cleaning is the process of detecting and 
% correcting (or removing) corrupt or inaccurate records from a record set, 
% table, or database and refers to identifying incomplete, incorrect, 
% inaccurate or irrelevant parts of the data and then replacing, 
% modifying, or deleting the dirty or coarse data.}
% \end{quote}
